%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[11pt, a4paper]{awesome-cv}

%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{cv/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-red}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Personal Data
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Essentials
\name{Sarojkumar "SK" B.}{Tondwalkar}
\address{14014 Eagle Chase Circle, Chantilly VA 20151, USA}
\mobile{(+1)571-488-0592} 
%%% Social
\email{sarojbt@yahoo.com}
%\homepage{www.posquit0.com}
%\github{posquit0}
\linkedin{sarojbt}
%%% Optionals
\position{Director Software Engineer{\enskip\cdotp\enskip}Cloud and Security Expert}
\quote{``Make the change that you want to see in the world."}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Letter Data (Cover Letter)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipient
  {Company Recruitment Team}
  {Walmart Inc.\\
%  1600 Amphitheatre Parkway\\Mountain View, CA 94043
  }
\letterdate{\today}
\lettertitle{Job Application for Director Software Engineering}
\letteropening{Dear Manager,}
\letterclosing{Sincerely,}
\letterenclosure[Attached]{Curriculum Vitae}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Content
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Make a footer for CV with three arguments(<left>, <center>, <right>)
\makecvfooter
  {\today}
  {Sarojkumar B. Tondwalkar~~~·~~~Cover Letter}
  {}

\begin{document}
%%% Make a header for CV using personal data
\makecvheader

%%% Make a title for Cover Letter using letter data
\makelettertitle

%%% Write content for your cover letter
\begin{cvletter}
\cvparagraph{About Me}
I am employed at Capital One in Northern Virginia as a Sr. Manager Software Engineering. I have led several teams across the organization.  Have strong experience in API development, using AWS Cloud, employing Agile methodology.  I have built DevOps teams. I have built highly secure and resilient systems. With more knowledge on the posted job role, I will be able to engage in a deeper discussion. 

\cvparagraph{Why Walmart?}
Recent tie up between Walmart and Capital One, has brought to my attention that Walmart is aiming to go even deeper in leveraging state of the art technology.  I am looking for growth and eager to contribute to the vision and growth of Walmart.

\cvparagraph{Why Me?}
I have the very strong hands-on experience of building DevOps teams of over 30 associates.  I have seen success in empowering and facilitating associates to give their best and bring innovation by looking for open source opportunities. I have mentoring and raised the bar in software delivery in all lines of business that I have worked. I have very strong experience in building well architect-ed systems. I would like to know more about this opportunity. 

\end{cvletter}

%%% Make a closing for Cover Letter using letter data
\makeletterclosing

\end{document}
